Kronos \& Krios: TBD

### 2017-05-09 paper/ms.tex
add caption for spec plots

>>>>

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.95\linewidth]{spec1.pdf}
  \caption{Selective segments of spectra of \sunanalog\ and \bizarreone.
    For each row, the continuum-normalized data and model are plotted in the upper panel,
    and the ratio (\bizarreone/\sunanalog) of data (gray) and model (black)
    are plotted in the lower panel.
  }
  \label{fig:spec1}
\end{figure}

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.95\linewidth]{spec2.pdf}
  \caption{Same as \figname~\ref{fig:spec1} but for smaller portions of spectra that are
    not dominated by \elem{Fe}. We mark elements that give rise to strong lines.
    The feature in the third column of the second row is a strong \elem{Li} line that was
    not modeled by \citealt{2016ApJS..225...32B}. This line was studied in a separate study
    \todo{CITE}.
  }
  \label{fig:spec2}
\end{figure}
